My title

### 2024-02-11 outputs/paper/paper.qmd
testing
Initial changes to the document to check test the data

@@

# Introduction

>>>>

scores = read_csv(
  file = here("outputs/data/all_scoredata.csv"),       
  show_col_types = FALSE
)
scores_2019 = read_csv(
  file = here("outputs/data/score_ohio.csv"),       
  show_col_types = FALSE
)

@@

```{r}
#| label: Vanshika-graphs
#| fig-cap: lets see
#| echo: false
# Plotting passing rates for each state
ggplot(scores, aes(x = state, y = pass, fill = state)) +
  geom_bar(stat = "identity") +
  labs(title = "Passing Rates Across Different States",
       x = "State",
       y = "Passing Rate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
# graph of all the passing rate all the different states

# Calculate the difference between passing rates
pass_diff <- scores$pass - mean(scores$pass)

# Plotting
ggplot(scores, aes(x = state, y = pass_diff, fill = state)) +
  geom_bar(stat = "identity") +
  labs(title = "Difference in Passing Rates Between States",
       x = "State",
       y = "Difference in Passing Rates") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# The lowest passing rates were Rhode Island

# graph for rode island and its unemployemnt during covid
# Plotting passing rates for each state
rhode_island_data <- subset(scores, state == "RI")
ggplot(scores, aes(x = state , y = unemployment, fill = state)) +
  geom_bar(stat = "identity") +
  labs(title = "unemployment Across Different States",
       x = "State",
       y = "Unemployemtn Rate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
# graph of all the passing rate all the different states

ggplot(scores, aes(x = state , y = cts_pass_advanced, fill = state)) +
  geom_bar(stat = "identity") +
  labs(title = "advanced Passing Rates Across Different States",
       x = "State",
       y = "Passing Rate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(scores, aes(x = state , y = cts_pass_proficient, fill = state)) +
  geom_bar(stat = "identity") +
  labs(title = "profient Passing Rates Across Different States",
       x = "State",
       y = "Passing Rate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(scores, aes(x = state , y = cts_pass_approaching, fill = state)) +
  geom_bar(stat = "identity") +
  labs(title = "approaching Passing Rates Across Different States",
       x = "State",
       y = "Passing Rate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(scores, aes(x = state , y = cts_pass_partially, fill = state)) +
  geom_bar(stat = "identity") +
  labs(title = "Partially Passing Rates Across Different States",
       x = "State",
       y = "Passing Rate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(scores, aes(x = state , y = cts_pass_below, fill = state)) +
  geom_bar(stat = "identity") +
  labs(title = "below Passing Rates Across Different States",
       x = "State",
       y = "Passing Rate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# DATA WITH ONLY 2019
ggplot(scores_2019, aes(x = state, y = pass, fill = state)) +
  geom_bar(stat = "identity") +
  labs(title = "Passing Rates In 2019",
       x = "State",
       y = "Passing Rate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```{r}
#| label: Vanshika-RI
#| fig-cap: lets see
#| echo: false
library(reshape2)
# Select relevant columns for correlation analysis
correlation_data <- scores[, c("pass", "participation", "share_black", "share_white", "share_hisp", "share_lunch", "unemployment")]

# Calculate correlation matrix
correlation_matrix <- cor(correlation_data, use="complete.obs")

# Convert the correlation matrix to a data frame
correlation_df <- melt(correlation_matrix)

# Plotting the correlation heatmap
correlation_heatmap <- ggplot(correlation_df, aes(Var1, Var2, fill=value)) +
  geom_tile(color="white") +
  scale_fill_gradient2(low="blue", mid="white", high="red", midpoint=0, limit=c(-1,1), space="Lab", name="Correlation") +
  theme_minimal() +
  labs(title = "Correlation Analysis: Heatmap of Correlation Coefficients",
       x = "Variables",
       y = "Variables") +
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

# Display the heatmap
correlation_heatmap

# Select relevant columns for correlation analysis
correlation_data <- scores[, c("share_inperson", "share_virtual", "share_hybrid", "pass", "participation", "share_black", "share_white", "share_hisp", "unemployment")]

# Calculate correlation matrix
correlation_matrix <- cor(correlation_data, use="complete.obs")

# Convert the correlation matrix to a data frame
correlation_df <- melt(correlation_matrix)

# Plotting the correlation heatmap with vertical x-axis labels
correlation_heatmap <- ggplot(correlation_df, aes(Var1, Var2, fill=value)) +
  geom_tile(color="white") +
  scale_fill_gradient2(low="blue", mid="white", high="red", midpoint=0, limit=c(-1,1), space="Lab", name="Correlation") +
  theme_minimal() +
  labs(title = "Correlation Analysis: Heatmap of Correlation Coefficients",
       x = "Variables",
       y = "Variables") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

# Display the heatmap
correlation_heatmap

# Select relevant columns for correlation analysis
correlation_data <- scores %>%
  select(state, participation, share_inperson)

# Calculate correlation matrix by grouping data by state and then calculating correlations
correlation_matrix <- correlation_data %>%
  group_by(state) %>%
  summarise(correlation = cor(participation, share_inperson))

# Plotting the correlation graph
correlation_graph <- ggplot(correlation_matrix, aes(x = state, y = correlation)) +
  geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
  labs(title = "Correlation between Participation Rate and Share In Person by State",
       x = "State",
       y = "Correlation") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Display the correlation graph
correlation_graph

# coorelation between virtual and participation
# Select relevant columns for correlation analysis
correlation_data <- scores %>%
  select(state, participation, share_virtual)

# Calculate correlation matrix by grouping data by state and then calculating correlations
correlation_matrix <- correlation_data %>%
  group_by(state) %>%
  summarise(correlation = cor(participation, share_virtual))

# Plotting the correlation graph
correlation_graph <- ggplot(correlation_matrix, aes(x = state, y = correlation)) +
  geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
  labs(title = "Correlation between Participation Rate and Share virtual by State",
       x = "State",
       y = "Correlation") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Display the correlation graph
correlation_graph

# corelation between pass and unemployemnt 
# Select relevant columns for correlation analysis
correlation_data <- scores %>%
  select(state, unemployment, pass)

# Calculate correlation matrix by grouping data by state and then calculating correlations
correlation_matrix <- correlation_data %>%
  group_by(state) %>%
  summarise(correlation = cor(unemployment, pass))

# Plotting the correlation graph
correlation_graph <- ggplot(correlation_matrix, aes(x = state, y = correlation)) +
  geom_bar(stat = "identity", fill = "purple", width = 0.5) +
  labs(title = "Correlation between Unemployement Rate and passing rate by State",
       x = "State",
       y = "Correlation") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Display the correlation graph
correlation_graph
```

```{r}
#| label: Random Graphs
#| fig-cap: lets see
#| echo: false

# Passing rate trends over different years and subjects
passing_rate_trends <- ggplot(scores, aes(x = year, y = pass, color = subject)) +
  geom_line() +
  labs(title = "Passing Rate Trends Over Different Years and Subjects",
       x = "Year",
       y = "Passing Rate",
       color = "Subject") +
  theme_minimal()

# Variations between different districts or states
passing_rate_variations <- ggplot(scores, aes(x = state, y = pass, fill = state)) +
  geom_boxplot() +
  labs(title = "Variations in Passing Rates Between Different States",
       x = "State",
       y = "Passing Rate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Display the graphs
passing_rate_trends
passing_rate_variations

# Investigating participation rates across districts or states
participation_rates <- ggplot(scores, aes(x = state, y = participation, fill = state)) +
  geom_boxplot() +
  labs(title = "Participation Rates Across Different States",
       x = "State",
       y = "Participation Rate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Display the graph
participation_rates

# Relationship between demographic factors and passing rates
demographic_analysis <- ggplot(scores, aes(x = share_black, y = pass)) +
  geom_point() +
  labs(title = "Relationship Between Percentage of Black Students and Passing Rate",
       x = "Percentage of Black Students",
       y = "Passing Rate") +
  theme_minimal()

# Display the graph
demographic_analysis

# Comparing passing rates between different subjects
subject_comparison <- ggplot(scores, aes(x = subject, y = pass, fill = subject)) +
  geom_boxplot() +
  labs(title = "Passing Rates Comparison Between Different Subjects",
       x = "Subject",
       y = "Passing Rate") +
  theme_minimal()

# Display the graph
subject_comparison

```
# Introduction
